\section{Preliminaries}
\label{sec:background}

\subsection{Networks of Timed Automata and Properties}

The paper follows standard timed-automata semantics~\cite{bengtsson2004timed}.
This section establishes the notation used for multi-property clock-bound repair.

\noindent\textbf{Definition 1 (Timed automaton).}
A timed automaton (TA) is a tuple
\begin{equation}
T=(L,\ell_0,C,\Sigma,\Theta,I),
\label{eq:ta}
\end{equation}
where $L$ is a finite set of locations, $\ell_0$ is the initial
location, $C$ is a finite set of clocks, $\Sigma$ is a set of action
labels, $\mathcal{B}(C)$ is the set of clock constraints over $C$,
$\Theta\subseteq L\times\mathcal{B}(C)\times\Sigma\times 2^C\times L$
is a finite set of transitions, and
$I:L\rightarrow\mathcal{B}(C)$ maps each location to a clock invariant.
A clock constraint is a conjunction of
atoms $x\sim b$, where $x\in C$, $\sim\in\{<,\leq,=,\geq,>\}$, and
$b\in\mathbb{R}_{\geq 0}$. A transition
$\theta=(\ell,g,a,R,\ell')$ moves from $\ell$ to $\ell'$ when guard
$g$ is satisfied, emits action $a$, and resets clocks in $R\subseteq C$.
As mentioned above, this work focuses on
repairing clock bounds. Specifically, a clock bound is the numerical
constant $b$ in an atomic clock constraint $x\sim b$ appearing in a
transition guard or location invariant.

\noindent\textbf{Definition 2 (NTA with property set).}
An NTA specification consists of a network of timed automata and the
properties that the network must satisfy:
\begin{equation}
\begin{aligned}
M &= (N,\Phi),\\
N &= T_1\parallel\cdots\parallel T_k,\\
\Phi &= \{\varphi_1,\ldots,\varphi_m\}.
\end{aligned}
\label{eq:nta-property-set}
\end{equation}
The network $N$ models a real-time system by composing
interacting timed automata, with synchronization semantics supplied by
the target modeling language, such as UPPAAL~\cite{larsen1997uppaal}.
The property set $\Phi$ is part of the system specification: it states
the timing and behavioral requirements that the NTA must satisfy. The
notation $N\models\Phi$ means that $N$ satisfies every property in
$\Phi$:
\begin{equation}
N\models\Phi
\quad\Longleftrightarrow\quad
\forall\varphi_i\in\Phi,\; N\models\varphi_i.
\label{eq:property-set-satisfaction}
\end{equation}

The repair problem considered here is restricted to timed safety
properties, which require a state predicate to hold in every reachable
state. In UPPAAL-style notation, such a property has the invariant form
$\texttt{A[]}\,p$, where $p$ is a state predicate composed of location
predicates and clock constraints. For example,
$\texttt{A[]}\,(\texttt{Controller.Waiting}\ \texttt{imply}\ x\leq 10)$
requires that clock $x$ never exceed 10 while the controller is in the
\texttt{Waiting} location.

\subsection{Timed Diagnostic Traces}

\noindent\textbf{Definition 3 (Timed diagnostic trace).}
Given an NTA specification $M=(N,\Phi)$ and a
property $\varphi\in\Phi$, a timed diagnostic trace (TDT) for
$\varphi$ is a feasible finite timed execution of $N$ that
reaches a state violating $\varphi$.
When verification of $\varphi$ fails, a real-time model checker can
generate a TDT as a counterexample. In UPPAAL, such a counterexample
consists of a sequence of states and transitions, together with clock
constraints describing the associated timing
information~\cite{larsen1997uppaal}.

In MPTA-Repair, each TDT is treated as a property-trace constraint:
the violated property identifies the requirement to be restored, and
the trace identifies the timed behavior that makes the violation
feasible. Section~\ref{sec:approach} uses such constraints from
multiple properties in a joint solving process.

\subsection{Functional Equivalence and Repair Acceptance}

Following TARTAR~\cite{kolbl2019clock}, we adopt equality of untimed
languages as the criterion for functional equivalence. Under this
criterion, a timing repair should neither remove existing functional
behavior of the original model nor introduce new functional behavior,
even though it changes timing constraints to eliminate violations.

\noindent\textbf{Definition 4 (Functional equivalence).}
For an NTA $N$, let $L_\mu(N)$ denote the untimed language obtained by
abstracting from delays while preserving the discrete behavior feasible
under the timing constraints. Two NTA models $N_1$ and $N_2$ are
functionally equivalent if
\begin{equation}
L_\mu(N_1)=L_\mu(N_2).
\end{equation}

\noindent\textbf{Definition 5 (Accepted repair).}
Let $M_{\mathit{bad}}=(N_{\mathit{bad}},\Phi)$ be
a faulty NTA specification. A candidate repair
$M_{\mathit{rep}}=(N_{\mathit{rep}},\Phi)$ is obtained by changing only
repairable clock bounds in guards and invariants. The candidate is
accepted as a repair if and only if
\begin{equation}
  N_{\mathit{rep}}
  \models
  \Phi
  \quad\land\quad
  L_\mu(N_{\mathit{bad}})
  =
  L_\mu(N_{\mathit{rep}}).
  \label{eq:accepted-repair}
\end{equation}
The first conjunct corresponds to full-property regression verification:
the model must satisfy the entire property set, not only the
property that produced the current TDT. The second conjunct is the
admissibility check based on untimed functional equivalence; it prevents
repairs that make properties true by disabling required functional
behavior. MPTA-Repair uses this accepted-repair condition as the global
validation criterion for candidates generated from local TDT evidence.
