\section{Implementation and Experimental Evaluation}
\label{sec:evaluation}

This section details the implementation of the MPTA-Repair framework
and systematically evaluates its practical effectiveness across both
standardized benchmark models and complex industrial case studies. To
clearly distinguish our targeted contribution while maintaining
practical applicability, our methodology strictly focuses on the
automated repair of numerical clock bounds within transition guards and
location invariants, deliberately avoiding arbitrary alterations to the
underlying discrete transition logic. This focused parametric repair
space is pragmatic for industrial contexts, because modifying clock
bounds can correct clerical modeling mistakes and provide useful
insights for redimensioning system time resources without disrupting the
intended functional design. Furthermore, we compare MPTA-Repair with a
specialized iterative baseline technique constructed by extending the
foundational TARTAR repair idea \cite{koelbl2020tartar} with a
sequential repair loop. This comparison demonstrates the necessity of
incorporating multi-property regression and multi-counterexample
analysis to prevent secondary errors during repair.

\subsection{Prototype Implementation}

We implemented MPTA-Repair as a highly integrated, incremental repair
pipeline built around a specialized timed-automata model parser, a
verification interface using UPPAAL \cite{larsen1997uppaal}, a
MaxSMT-based repair backend powered by Z3 \cite{demoura2008z3}, a
dedicated admissibility checker, and an overarching iterative refinement
control loop. Initially, the repair frontend parses the faulty model to
extract editable clock-bound variables embedded within transition guards
and location invariants. The trace analyzer then maps observed
diagnostic traces to these extracted variables. Concurrently, the
relation analyzer establishes dependencies among the specified
properties, generated traces, and localized repair sites in order to
prioritize candidate generation and reduce the computational search
space.

Once the MaxSMT backend synthesizes a viable candidate assignment, the
model writer instantiates the corresponding repaired model. Final
candidate acceptance relies on two consecutive validation gates designed
to guarantee both timing correctness and behavioral fidelity. The first
gate performs full-property regression verification through UPPAAL to
ensure that no collateral property violations occur. The second gate is
an admissibility check for functional equivalence following the
TARTAR-style criterion \cite{koelbl2019clock}. This module constructs
untimed automata from both the original and repaired models and performs
a comparative language-equivalence test. The system rejects any
candidate that inadvertently adds or removes functional untimed
behavior. Whenever either validation gate rejects a candidate, the
control loop captures the newly exposed diagnostic traces and feeds them
back into the relation analyzer. This initiates an incremental,
counterexample-guided refinement iteration that further constrains the
MaxSMT solver with updated evidence until a globally correct and
admissible repair is found or the search budget is exhausted.

\subsection{Evaluation Strategy and Datasets}

To evaluate the proposed framework, we use two dataset groups designed
to exercise different operational dimensions. The benchmark dataset
contains established timed-automata models from standard UPPAAL and XTA
sources, including protocol-style models such as CSMA/CD and FDDI.
These models provide structural diversity and support comparison with
existing single-trace repair settings. To assess practical
applicability, the industry dataset contains industrial case studies
with multi-component networks and domain-level timing requirements,
including railway communication protocols \cite{basile2021unisig},
automotive gear control \cite{lindahl1998gear}, and cardiac pacing
\cite{jiang2012pacemaker}. Unlike many standard benchmarks, these
industrial models typically include between three and nine coupled
timing properties. The two dataset groups therefore test both basic
algorithmic behavior and the more difficult synchronization and
property-interaction patterns found in practical industrial models.

Because naturally occurring faulty timed-automata models are scarce, we
use a mutation-based evaluation strategy to synthesize faulty instances
\cite{jia2011mutation}. Consistent with the repair space defined in
this paper, fault injection strictly modifies numerical clock-bound
constants in guards and invariants and deliberately excludes arbitrary
structural logic changes. Simple mutants contain a localized
single-point modification. Complex mutants are constructed using a
two-fault effective mutation strategy, where each complex instance
combines two non-redundant single-point faults. These combinations are
filtered to remove trivial cases and retain only instances in which both
faults contribute to the resulting property violation. All retained
mutants are checked to ensure that they remain syntactically valid,
violate at least one selected timing safety specification, and pass a
preliminary admissibility screen so that the original non-timing
functional behavior is not destroyed before repair begins.

We compare MPTA-Repair with an adapted iterative TARTAR-style baseline
\cite{koelbl2020tartar}. To keep the comparison fair, the baseline is
given the same full-property regression and admissibility validation
gates used by MPTA-Repair. The key methodological difference is that the
baseline still derives repairs from one property or diagnostic trace at
a time. Since it lacks the joint multi-counterexample relation analysis
used by MPTA-Repair, it is more prone to localized optimization and
overfitting to isolated fault paths. This comparison highlights the
benefit of evaluating properties, counterexamples, and repair variables
as joint repair evidence.

\subsection{Experimental Results}

The experimental evaluation shows that MPTA-Repair outperforms the
iterative baseline, particularly on complex industrial models. On the
standardized benchmark dataset, the baseline repairs 72\% of the cases,
whereas MPTA-Repair achieves a 93\% success rate. The performance gap
becomes larger on the industry dataset: the baseline repairs 20\% of the
cases, while MPTA-Repair repairs 76\%. These results suggest that the
proposed workflow remains effective on established timed-automata
benchmarks and is substantially more robust when properties and traces
interact in industrial models.

\input{tables/overall-results}

The baseline remains competitive on simpler benchmark models where
timing errors are concentrated on isolated guards or invariants. In such
localized cases, a single diagnostic trace often provides enough
evidence to infer a useful clock-bound repair. However, even within
standard benchmarks with shared multi-channel structures, such as FDDI
protocol models, MPTA-Repair is more robust because it actively prevents
single-trace overfitting. This advantage is more pronounced in
industrial models with interacting concurrent components, urgent or
broadcast synchronization channels, observer templates, and array-based
modeling constructs. In these settings, local baseline repairs
frequently fail later global validation checks. We observed two common
causes: the baseline does not explicitly optimize edit magnitude and can
therefore generate extreme candidate bounds that fail admissibility, and
it must satisfy the regression pressure imposed by three to nine coupled
domain properties without jointly analyzing their counterexamples.

MPTA-Repair succeeds more often because of two architectural advantages.
First, multi-counterexample accumulation reduces overfitting to one
timed diagnostic trace. A single trace typically exposes only one timing
realization of a deeper defect. By accumulating and analyzing diagnostic
traces from multiple operational modes, MPTA-Repair can synthesize small
joint edit sets that address the shared timing fault without leaving
related faulty traces feasible.

Second, relation-guided optimization works together with precise MaxSMT
objectives to improve candidate quality. In the ablation analysis,
removing this optimization increased the frequency of regression
failures. By identifying diagnostic traces that share path fragments or
repair variables, the solver can focus on numerical clock bounds close
to the observed violations while also penalizing large edit magnitudes.
Successful repairs therefore typically modify only one or two critical
clock bounds, which makes the resulting suggestions easier for human
engineers to inspect and validate.

\subsection{Discussion and Practical Lessons}

The evaluation highlights several lessons for applying automated repair
to industrial timed automata. First, full-property regression testing is
necessary. Industrial properties are often highly interdependent: a
localized fix that satisfies a liveness-like response monitor can
violate a separate safety monitor that constrains maximum waiting time.
MPTA-Repair avoids accepting such behavioral regressions by treating
restoration of the full property set as a global objective rather than
as a sequence of isolated local patches.

Second, admissibility changes the meaning of repair success. Without
checking structural and functional equivalence, a solver could satisfy a
timed property by disabling intended behavior, for example by preventing
a critical action or blocking a necessary communication response. Such a
candidate may eliminate the targeted timed diagnostic trace, but it is
not a valid repair for an industrial model. The admissibility check
therefore prevents property satisfaction from being achieved through
unacceptable loss of untimed behavior.

Finally, the unrepaired cases reveal several limits of the current
repair space. Solver, verification, and admissibility timeouts account
for only part of the failures, and some models use syntax outside the
supported fragment. In highly coupled domains such as cardiac pacing,
some errors require paired and consistent adjustments across both guards
and invariants, which increases the difficulty of the search. Incomplete
diagnostic trace coverage returned by the verification engine can also
lead to residual overfitting. Most fundamentally, some complex cases do
not appear to have a feasible candidate within numerical clock-bound
edits alone. These limitations suggest that future work should consider
broader repair actions, such as changing synchronization labels,
adjusting clock resets, or redesigning discrete data updates, while
still preserving the functional intent of the model.
